A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-19 main.tex
Wrote connection degree and free variables.

\newcommand{\G}{\Gamma}
\newcommand{\D}{\Delta}
\newcommand{\V}{\vdash}
\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
\newcommand{\iskind}{\text{\ kind}}
\newcommand{\TW}{\triangleright}
\newcommand{\TWL}{\triangleleft}
\newcommand{\F}{\forall}
\newcommand{\TB}{\blacktriangleright}
\newcommand{\TBL}{\blacktriangleleft}
\newcommand{\E}{\equiv}
\newcommand{\FV}{\text{FV}}
\newcommand{\FTV}{\text{FTV}}

@@

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organaization of the Paper}

@@

% 演算子の結合順序

@@

@@

In this section, we define full reduction for \LMD.
Before giving the definition of reduction, we define two substitutions.
Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its defnition here.
Substituition $M[\alpha \mapsto \epsilon]$ is defined below.

>>>>

\newcommand{\G}{\Gamma}
\newcommand{\D}{\Delta}
\newcommand{\V}{\vdash}
\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
\newcommand{\iskind}{\text{\ kind}}
\newcommand{\TW}{\triangleright}
\newcommand{\TWL}{\triangleleft}
\newcommand{\F}{\forall}
\newcommand{\TB}{\blacktriangleright}
\newcommand{\TBL}{\blacktriangleleft}
\newcommand{\E}{\equiv}
\newcommand{\FV}{\text{FV}}
\newcommand{\FTV}{\text{FSV}}

@@

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organization of the Paper}

@@

% 演算子の結合順序
Connection degree of $\TB_\alpha, \TBL_\alpha, \%_\alpha$ is stronger than the two forms of applications
and applications are left-associative
and two abstractions extends as far to the right as possible.

@@

As usual, the variable $x$ is bound in $\lambda x:\tau.M$
and the transition variable $\alpha$ is bound in $\Lambda \alpha.M$.
We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
We omit their definitions.

@@

In this section, we define full reduction for \LMD.
Before giving the definition of reduction, we define two substitutions.
Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
Substituition $M[\alpha \mapsto \epsilon]$ is defined below.
